### 2024-09-23 paper/paper.qmd
changed

---
title: "Tornto annual energy consumption"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-09-24 paper/paper.qmd
updated

@@
 ---
-title: "Tornto annual energy consumption"
-subtitle: "My subtitle if needed"
+title: "Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Irene Liu
+thanks: "Code and data are available at: https://github.com/zilin1017/Toronto_annual_energy_consumption.git."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study examines the relationship between building size(GFA) and electricity consumption in Toronto's public facilities.
+Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage.
+Larger facilities, particularly healthcare centers, demonstrate higher energy consumption per square meter.
+These results help inform efforts to improve energy management in Toronto’s public buildings."
 format: pdf

### 2024-09-24 paper/paper.qmd
changed

@@
 # Introduction
+
+Public infrastructure, including schools, libraries, healthcare centers, and government offices, forms the backbone of urban services in any modern city.
+As Toronto continues to expand, managing electricity usage in public buildings becomes increasingly critical.
+Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation \cite{droege2018urban}.
 

### 2024-09-24 scripts/01-download_data.R
changed code and name the data

@@ -10,17 +10,19 @@
 
 #### Workspace setup ####
 library(opendatatoronto)
-library(tidyverse)
-# [...UPDATE THIS...]
-
+library(dplyr)
+library(readr)
+library(readxl)
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
+consumption-data <- download.file("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/0600cad8-d024-483b-a9a8-ecfc3e32e375/resource/9353c7fe-d33d-47e9-9934-c6ca8bf04c75/download/annual-energy-consumption-data-2021.xlsx", 
+              destfile = "~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", 
+              mode = "wb")
 
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+
+consumption_data <- read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx")
+
+head(consumption_data)
 
          

### 2024-09-24 scripts/01-download_data.R
download data and named

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from  opendatatoronto
+# Author: Irene Liu
+# Date: 24 September 2024
+# Contact: liuzilin.liu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 
 #### Workspace setup ####

### 2024-09-24 scripts/00-simulate_data.R
code updated

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from  opendatatoronto
+# Author: Irene Liu
+# Date: 24 September 2024
+# Contact: liuzilin.liu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: None
 
 
 #### Workspace setup ####
@@ -13,7 +12,17 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+my_data <- readxl::read_excel("data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5) # 记得改
+my_data <- my_data|>
+  dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`)) |>
+  dplyr::mutate(ID = `Portfolio Manager Property ID`,
+                Area = `Property GFA - Self-Reported (m²)`,
+                kWh = `Electricity Use - Grid Purchase (kWh)`) |>
+  dplyr::mutate(kWh = as.numeric(kWh)) |>
+  dplyr::filter(Area < 2500 & Area > 30) |>
+  dplyr::mutate(log_Area = log(Area))
+
+write.csv(my_data, "data/analysis_data/simulated_analysis_data.csv")
 
 
 

### 2024-09-24 scripts/01-download_data.R

@@ -1,10 +1,4 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from  opendatatoronto
-# Author: Irene Liu
-# Date: 24 September 2024
-# Contact: liuzilin.liu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
+
 
 
 #### Workspace setup ####
@@ -13,15 +7,15 @@ library(dplyr)
 library(readr)
 library(readxl)
 #### Download data ####
-consumption-data <- download.file("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/0600cad8-d024-483b-a9a8-ecfc3e32e375/resource/9353c7fe-d33d-47e9-9934-c6ca8bf04c75/download/annual-energy-consumption-data-2021.xlsx", 
+download.file("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/0600cad8-d024-483b-a9a8-ecfc3e32e375/resource/9353c7fe-d33d-47e9-9934-c6ca8bf04c75/download/annual-energy-consumption-data-2021.xlsx", 
               destfile = "~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", 
               mode = "wb")
 
 
 #### Save data ####
 
-consumption_data <- read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx")
+raw_data<- read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx")
 
-head(consumption_data)
+head(raw_data)
 
-         
+write_csv(raw_data, "data/raw_data/raw_data.csv")       

### 2024-09-24 scripts/00-simulate_data.R
changed

@@ -12,7 +12,7 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Simulate data ####
-my_data <- readxl::read_excel("data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5) # 记得改
+my_data <- readxl::read_excel("data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
 my_data <- my_data|>
   dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`)) |>
   dplyr::mutate(ID = `Portfolio Manager Property ID`,

### 2024-09-24 paper/paper.qmd
change data name and code

@@
 As Toronto continues to expand, managing electricity usage in public buildings becomes increasingly critical.
-Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation \cite{droege2018urban}.
+Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation[@droege2018urban].
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+One of the primary determinants of electricity consumption is building size, commonly measured as Gross Floor Area (GFA).
+Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2019occupant].
+As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2011managing].
 
-The remainder of this paper is structured as follows. @sec-data....
+Several studies have shown that energy efficiency measures in public buildings can lead to significant reductions in electricity consumption.
+For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@eto2012impact; @santamouris2016innovative].
+
+This paper explores the relationship between Property GFA (m²) and electricity usage (kWh) in over 500 public facilities in Toronto.
+The study aims to identify patterns in electricity consumption and provide insights for optimizing energy use in Toronto's public sector.
 
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-Area
+#| fig-cap: Density Plot for Property Area in Toronto
 #| echo: false
@@
 
+Talk way more about it.
+
 ```{r}
-#| label: fig-planes
+#| label: none
 #| fig-cap: Relationship between wing length and width
 #| echo: false
+#| message: false
 #| warning: false
-#| message: false
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+analysis_data <- read.csv("/Users/liuzilin/Desktop/Toronto_annual_energy_consumption/data/analysis_data/analysis_data.csv")
 
 analysis_data |>
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+  ggplot(aes(x=log_Area)) +
+  geom_histogram(aes(y= ..density..,fill = "pink")) +
+  geom_density() +
+  ggtitle("Density Plot for Property Area in Toronto")
 ```
-
-Talk way more about it.
 
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-09-26 scripts/00-simulate_data.R
updated

@@ -22,7 +22,7 @@ my_data <- my_data|>
   dplyr::filter(Area < 2500 & Area > 30) |>
   dplyr::mutate(log_Area = log(Area))
 
-write.csv(my_data, "data/analysis_data/simulated_analysis_data.csv")
+write.csv(my_data, "data/analysis_data/analysis_data.csv")
 
 
 

### 2024-09-26 paper/paper.qmd
plot added

@@
 
+#install.packages("opendatatoronto")
+#install.packages("tidyverse")
 library(tidyverse)
@@
 One of the primary determinants of electricity consumption is building size, commonly measured as Gross Floor Area (GFA).
-Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2019occupant].
-As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2011managing].
+Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2016occupant].
+As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2009managing].
 
 Several studies have shown that energy efficiency measures in public buildings can lead to significant reductions in electricity consumption.
-For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@eto2012impact; @santamouris2016innovative].
+For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@scott2008impact].
 
@@
   coord_flip()
+
+# Load necessary libraries
+library(readxl)
+library(ggplot2)
+library(tidyverse)
+
+# Relative path, assuming the project root directory is the current working directory
+annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
+
+# Select and mutate columns, assigning the result back to the original data
+annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 |>
+  dplyr::select(`Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`,  `City`) |>
+  dplyr::mutate(Area = `Property GFA - Self-Reported (m²)`,
+                kWh = `Electricity Use - Grid Purchase (kWh)`,
+                City = `City`)  # Ensure City is the correct column name without quotes
+
+# 基于数据的分面调整，并移除不必要的元素
+annual_energy_consumption_data_2021 %>%
+  ggplot(aes(x = Area, y = kWh, color = City)) +
+  geom_point(alpha = 0.5) + # 设置透明度以减少重叠的影响
+  geom_smooth(method = "lm", se = FALSE) +
+  facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
+  ggtitle("Electricity Usage vs Building Size by Facility Type") +
+  xlab("Building Size (GFA in m²)") +
+  ylab("Electricity Usage (kWh)") +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_blank(),  # 去掉y轴的数字
+    axis.ticks.y = element_blank(),  # 去掉y轴的刻度
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+# Load necessary libraries
+library(readxl)
+library(ggplot2)
+library(dplyr)
+
+# Read the data from Excel
+annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
+
+# Reclassify 'Other' types into a single 'Other' category
+annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 %>%
+  mutate(Property_Type = case_when(
+    grepl("Other", `Primary Property Type - Self Selected`) ~ "Other",
+    TRUE ~ `Primary Property Type - Self Selected`
+  ))
+
+# Plotting the data
+ggplot(annual_energy_consumption_data_2021, aes(x = `Property GFA - Self-Reported (m²)`, y = `Electricity Use - Grid Purchase (kWh)`, color = Property_Type)) +
+  geom_point(alpha = 0.5) + # Set transparency to avoid overlapping
+  geom_smooth(method = "lm", se = FALSE) +
+  facet_wrap(~ Property_Type, scales = "free") + # Facet based on Property_Type
+  ggtitle("Electricity Usage vs Building Size by Facility Type") +
+  xlab("Building Size (GFA in m²)") +
+  ylab("Electricity Usage (kWh)") +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_blank(), # Remove y-axis numbers
+    axis.ticks.y = element_blank(), # Remove y-axis ticks
+    axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis text
+  )
+
 ```
@@
 
+library(ggplot2)
+
 analysis_data <- read.csv("/Users/liuzilin/Desktop/Toronto_annual_energy_consumption/data/analysis_data/analysis_data.csv")
@@
   ggtitle("Density Plot for Property Area in Toronto")
+
+```
+
+```{r}
+#| label: second
+#| fig-cap: Relationship between ...
+#| echo: false
+#| message: false
+#| warning: false
+
+# Filter out zero or negative values (if needed)
+
+analysis_data <- analysis_data |> 
+  dplyr::filter(kWh > 0)
+
+# Plot the histogram and density
+analysis_data |>
+  ggplot(aes(x = kWh)) +
+  geom_histogram(aes(y = ..density..), fill = "orange", binwidth = 250000) +  # Adjust bin width
+  geom_density() +
+  ggtitle("Density Plot for Electricity Use in Toronto") +
+  theme_minimal()
+
 ```

### 2024-09-26 paper/paper.qmd
updated 3 data graph,choose 1

@@
 date-format: long
-abstract: "This study examines the relationship between building size(GFA) and electricity consumption in Toronto's public facilities.
+abstract: "This study examines the relationship between building size(m²) and electricity consumption(kWh) in Toronto's public facilities.
 Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage.
@@
 
+### graph1 ##
 # Load necessary libraries
@@
   facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
-  ggtitle("Electricity Usage vs Building Size by Facility Type") +
+  ggtitle("Electricity Usage vs Building Size by City") +
   xlab("Building Size (GFA in m²)") +
@@
 
+###2##
 # Load necessary libraries
@@
   )
+
+##graph3##
+
+# 使用柱状图展示不同建筑类型的总用电量
+ggplot(annual_energy_consumption_data_2021, aes(x = Property_Type, y = `Electricity Use - Grid Purchase (kWh)`, fill = Property_Type)) +
+  geom_bar(stat = "identity") +
+  ggtitle("Total Electricity Usage by Property Type") +
+  xlab("Property Type") +
+  ylab("Total Electricity Usage (kWh)") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 10),
+    axis.text.y = element_blank(), # Remove y-axis numbers
+    axis.ticks.y = element_blank(), # Remove y-axis ticks
+    axis.text.x = element_text(angle = 65, hjust = 1, size=6),
+    legend.key.size = unit(0.3, "cm"),
+    legend.text = element_text(size = 5))
 

### 2024-09-26 paper/paper.qmd
updated 3 data graph,choose 1

@@
 date-format: long
-abstract: "This study examines the relationship between building size(m²) and electricity consumption(kWh) in Toronto's public facilities.
+abstract: "This study examines the relationship between building size(GFA) and electricity consumption in Toronto's public facilities.
 Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage.

### 2024-09-26 scripts/01-download_data.R
updated code

@@ -4,18 +4,30 @@
 #### Workspace setup ####
 library(opendatatoronto)
 library(dplyr)
-library(readr)
-library(readxl)
-#### Download data ####
-download.file("https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/0600cad8-d024-483b-a9a8-ecfc3e32e375/resource/9353c7fe-d33d-47e9-9934-c6ca8bf04c75/download/annual-energy-consumption-data-2021.xlsx", 
-              destfile = "~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", 
-              mode = "wb")
 
+#### Download data ####
+
+# get package
+package <- show_package("0600cad8-d024-483b-a9a8-ecfc3e32e375")
+package
+
+# get all resources for this package
+resources <- list_package_resources("0600cad8-d024-483b-a9a8-ecfc3e32e375")
+
+# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
+datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
 
 #### Save data ####
 
-raw_data<- read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx")
+resource_id <- "9353c7fe-d33d-47e9-9934-c6ca8bf04c75"
+
+# Download the data
+raw_data <- get_resource(resource_id)
+
+# Save it as a CSV (if needed)
+write_csv(raw_data, "data/raw_data/raw_data.csv")
+
+# View the data
 
 head(raw_data)
 
-write_csv(raw_data, "data/raw_data/raw_data.csv")       

### 2024-09-27 scripts/00-simulate_data.R
change the simulate_data code

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from  opendatatoronto
 # Author: Irene Liu
-# Date: 24 September 2024
+# Date: 26 September 2024
 # Contact: liuzilin.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: None
@@ -12,17 +12,38 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Simulate data ####
-my_data <- readxl::read_excel("data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
-my_data <- my_data|>
-  dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`)) |>
-  dplyr::mutate(ID = `Portfolio Manager Property ID`,
-                Area = `Property GFA - Self-Reported (m²)`,
-                kWh = `Electricity Use - Grid Purchase (kWh)`) |>
-  dplyr::mutate(kWh = as.numeric(kWh)) |>
-  dplyr::filter(Area < 2500 & Area > 30) |>
-  dplyr::mutate(log_Area = log(Area))
+# Simulate data
+set.seed(30)
 
-write.csv(my_data, "data/analysis_data/analysis_data.csv")
+# Define the number of random entries you want to generate
+number_of_entries <- 1000
+
+# Define constraints for your data (adjust based on your needs)
+min_area <- 30
+max_area <- 2500
+min_kWh <- 100
+max_kWh <- 22000000
+
+# Simulate random data for 'dates', 'Area', 'kWh', and 'Property_Type'
+simulated_data <- tibble(
+  ID = seq(1, number_of_entries),  # Simulated IDs
+  Area = runif(n = number_of_entries, min = min_area, max = max_area),  # Random areas
+  kWh = runif(n = number_of_entries, min = min_kWh, max = max_kWh),  # Random electricity usage
+  Property_Type = sample(c("Library", "Office", "Fire Station", "Heated Swimming Pool", "Other"), 
+                         size = number_of_entries, replace = TRUE)  # Random property types
+)
+
+# Apply any additional transformations (e.g., filtering)
+simulated_data <- simulated_data %>%
+  filter(Area < 2500 & Area > 30) %>%
+  mutate(log_Area = log(Area))
+
+# View the first few rows of the simulated dataset
+head(simulated_data)
[…]

### 2024-09-27 paper/paper.qmd

--- 2024-09-26 paper/paper.qmd
@@
 
-# 使用柱状图展示不同建筑类型的总用电量
-ggplot(annual_energy_consumption_data_2021, aes(x = Property_Type, y = `Electricity Use - Grid Purchase (kWh)`, fill = Property_Type)) +
+library(ggplot2)
+library(dplyr)
+
+analysis_data <- read.csv("data/analysis_data/analysis_data.csv")
+
+# Reclassify 'Other' types into a single 'Other' category
+##analysis_data <- analysis_data %>%
+##  mutate(percentage = kWh / sum(kWh) * 100)
+analysis_data <- analysis_data %>%
+  mutate(Property_Type = case_when(
+    grepl("Other", `Primary Property Type - Self Selected`) ~ "Other",
+    TRUE ~ `Primary Property Type - Self Selected`
+  ))
+kWh_count <- analysis_data |>
+  group_by(Property_Type)|>
+  summarise(kWh = n()) |>
+  arrange(desc(kWh))
+
+ggplot(kWh_count, aes(x = Property_Type, y = kWh, fill = Property_Type)) +
   geom_bar(stat = "identity") +
+  geom_text(aes(label = paste0(round(kWh/sum(kWh) *100 , 1), "%")), vjust=-0.5) +
   ggtitle("Total Electricity Usage by Property Type") +

### 2024-09-27 scripts/02-data_cleaning.R
updated data cleaning

@@ -1,44 +1,30 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data recorded by two into an analysis data
+# Author: Irene Liu
+# Date: 26 September 2024
+# Contact: liuzilin.liu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Need to have downloaded the data
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("data/raw_data/raw_data.csv", skip=5)
 
 cleaned_data <-
   raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+  dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`),`Primary Property Type - Self Selected`) |>
[…]

### 2024-09-27 scripts/02-data_cleaning.R
updated code

@@ -9,22 +9,23 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
+library(readr)
 
 #### Clean data ####
 raw_data <- read_csv("data/raw_data/raw_data.csv", skip=5)
 
-cleaned_data <-
-  raw_data |>
-  dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`),`Primary Property Type - Self Selected`) |>
+cleaned_data <-raw_data |>
+  dplyr::select(c(`Portfolio Manager Property ID`, `Property GFA - Self-Reported (m²)`, 
+`Electricity Use - Grid Purchase (kWh)`), `Primary Property Type - Self Selected`) |>
   dplyr::mutate(ID = `Portfolio Manager Property ID`,
                 Area = `Property GFA - Self-Reported (m²)`,
                 kWh = `Electricity Use - Grid Purchase (kWh)`,
                 Property_Type = `Primary Property Type - Self Selected` )|>
   dplyr::mutate(kWh = as.numeric(kWh)) |>
   dplyr::filter(Area < 2500 & Area > 30) |>
-  dplyr::mutate(log_Area = log(Area))
+  dplyr::mutate(log_Area = log(Area))|>
+  dplyr::arrange(ID)
 
 #### Save data ####
 write.csv(cleaned_data, "data/analysis_data/analysis_data.csv")
-
 

### 2024-09-27 paper/paper.qmd
updated

--- 2024-09-26 paper/paper.qmd
@@
 format: pdf
+toc: true
 number-sections: true
@@
 
-#install.packages("opendatatoronto")
-#install.packages("tidyverse")
+##install the packages
+##install.packages("opendatatoronto")
+##install.packages("tidyverse")
+##install.packages("knitr")
+
 library(tidyverse)
-library(palmerpenguins)
+library(knitr)
+library(dplyr)
+library(ggplot2)
+library(readr)
+
 ```
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+## Raw data
+The data used in this paper came from the OpenData Toronto portal through the library [@opendt].
+Data were cleaned and analyzed using the open source statistical programming language R [@citeR].
+The particular data set used to analyze the Consumption of Energy is the Annual Energy Consumption Data in 2021 [@2021datatoronto].
+The following packages helped with the data analysis: tidyverse [@tidyverse], here [@here]), dplyr [@dplyr] and ggplot2 [@ggplot] was use for making graphics.
+All data analysis was conducted using R [@citeR].
+
+The data used in this analysis comes from the City of Toronto's Open Data Portal[@opendt], specifically focusing on energy consumption across various property types in Toronto for the year 2021[@2021datatoronto].
+The dataset consists of 1,802 unique entries, each representing a specific property in various regions of Toronto.
+For each property, the data captures critical metrics such as the building size, self-reported in gross floor area (GFA) in square meters (m²), and the total electricity consumption, measured in kilowatt-hours (kWh), purchased from the grid.
+No personal or property-specific information is included.
+The data was last updated on July 4, 2023, and helps understand energy usage trends across different building types in Toronto.
+
+## Cleaned Data
+
+The cleaning process focused on removing irrelevant or incomplete data to ensure the dataset was suitable for analyzing electricity consumption patterns in Toronto's public sector.
+Missing values(NA) were removed during the data cleaning process, particularly those related to electricity usage.
+And buildings that did not meet the size criteria (less than 30 square meters or greater than 2,500 square meters) were also filtered out.Additionally, variables irrelevant to the study’s focus were also omitted.
+Furthermore, the cleaned data retains only the key variables required for the analysis: property type, electricity use, floor area, and log-transformed area.
+This ensures that the final dataset is both accurate and relevant for understanding electricity consumption trends across different public facilities in Toronto.
+
+A sample of the cleaned data can be seen in @tbl-1.
+The cleaned analysis dataset is loaded using the R programming language [@citeR].
+The folder structure for this analysis is also inherited from Professor Rohan Alexander [@rohan].
+Figures and tables are then generated using the knitr [@knitr] and tidyverse [@tidyverse] packages.
+
+```{r}
+#| label: tbl-1
+#| tbl-cap: Sample of cleaned data
+#| echo: false
+
+analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
+
+analysis_data_subset <- analysis_data[ c("Property_Type", "kWh", "Area", "log_Area")]
+
+filtered_data <- analysis_data_subset|>
+  filter(!is.na(kWh) & kWh != "NA") |>   
+  distinct(Property_Type, .keep_all = TRUE)
+
+kable(
+  head(filtered_data, 6), 
+  col.names = c("Property Type", "Electricity Use (kWh)", "Area (m²)", "Log of Area (m²)"),
+  align = c("l", "c", "c", "c","c")
+)
+
+```
+
+## Data Analysis
 
@@
 #| echo: false
+#| message: false
+#| warning: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+raw_data <- read_csv(here::here("data/raw_data/raw_data.csv"), skip=5)
+analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
 
-### graph1 ##
-# Load necessary libraries
-library(readxl)
-library(ggplot2)
-library(tidyverse)
-
-# Relative path, assuming the project root directory is the current working directory
-annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
-
-# Select and mutate columns, assigning the result back to the original data
-annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 |>
-  dplyr::select(`Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`,  `City`) |>
+annual_energy_consumption_data_2021 <- raw_data |>
+  dplyr::select(`Property GFA - Self-Reported (m²)`, `Electricity Use - Grid Purchase (kWh)`,  `City`)|>
   dplyr::mutate(Area = `Property GFA - Self-Reported (m²)`,
                 kWh = `Electricity Use - Grid Purchase (kWh)`,
-                City = `City`)  # Ensure City is the correct column name without quotes
+                City = `City`)
 
-# 基于数据的分面调整，并移除不必要的元素
 annual_energy_consumption_data_2021 %>%
   ggplot(aes(x = Area, y = kWh, color = City)) +
-  geom_point(alpha = 0.5) + # 设置透明度以减少重叠的影响
+  geom_point(alpha = 0.5) + 
   geom_smooth(method = "lm", se = FALSE) +
-  facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
+  facet_wrap(~ City, scales = "free") + 
   ggtitle("Electricity Usage vs Building Size by City") +
@@
   theme(
-    axis.text.y = element_blank(),  # 去掉y轴的数字
-    axis.ticks.y = element_blank(),  # 去掉y轴的刻度
-    axis.text.x = element_text(angle = 45, hjust = 1)
+    axis.ticks.y = element_blank(),  
+    axis.text.y = element_blank(),
+    axis.text.x = element_text(angle = 45, hjust = 1, size=4.5),
+    panel.grid.major = element_blank(), 
+    panel.grid.minor = element_blank()
   )
 
-###2##
-# Load necessary libraries
-library(readxl)
-library(ggplot2)
-library(dplyr)
+```
 
-# Read the data from Excel
-annual_energy_consumption_data_2021 <- readxl::read_excel("~/Desktop/Toronto_annual_energy_consumption/data/raw_data/annual-energy-consumption-data-2021.xlsx", skip = 5)
+```{r}
+#| label: fig-Property
+#| fig-cap: Percentage Electricity Usage by Properties 
+#| echo: false
+#| message: false
+#| warning: false
 
-# Reclassify 'Other' types into a single 'Other' category
-annual_energy_consumption_data_2021 <- annual_energy_consumption_data_2021 %>%
+raw_data <- read_csv(here::here("data/raw_data/raw_data.csv"), skip=5)
+analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
+
+analysis_data <- analysis_data |>
   mutate(Property_Type = case_when(
-    grepl("Other", `Primary Property Type - Self Selected`) ~ "Other",
-    TRUE ~ `Primary Property Type - Self Selected`
+    grepl("Other", `Property_Type`) ~ "Other",
+    TRUE ~ `Property_Type`
   ))
+kWh_count <- analysis_data |>
+  group_by(Property_Type)|>
+  summarise(kWh = n()) |>
+  arrange(desc(kWh))
 
-# Plotting the data
-ggplot(annual_energy_consumption_data_2021, aes(x = `Property GFA - Self-Reported (m²)`, y = `Electricity Use - Grid Purchase (kWh)`, color = Property_Type)) +
-  geom_point(alpha = 0.5) + # Set transparency to avoid overlapping
-  geom_smooth(method = "lm", se = FALSE) +
-  facet_wrap(~ Property_Type, scales = "free") + # Facet based on Property_Type
-  ggtitle("Electricity Usage vs Building Size by Facility Type") +
-  xlab("Building Size (GFA in m²)") +
-  ylab("Electricity Usage (kWh)") +
-  theme_minimal() +
-  theme(
-    axis.text.y = element_blank(), # Remove y-axis numbers
-    axis.ticks.y = element_blank(), # Remove y-axis ticks
-    axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis text
-  )
-
-##graph3##
-
-# 使用柱状图展示不同建筑类型的总用电量
-ggplot(annual_energy_consumption_data_2021, aes(x = Property_Type, y = `Electricity Use - Grid Purchase (kWh)`, fill = Property_Type)) +
+ggplot(kWh_count, aes(x = Property_Type, y = kWh, fill = Property_Type)) +
   geom_bar(stat = "identity") +
+  geom_text(aes(label = paste0(round(kWh/sum(kWh) *100 , 1), "%")), vjust=0.2, size = 2) +
   ggtitle("Total Electricity Usage by Property Type") +
@@
   theme(
-    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 10),
-    axis.text.y = element_blank(), # Remove y-axis numbers
-    axis.ticks.y = element_blank(), # Remove y-axis ticks
+    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 8),
+    axis.text.y = element_blank(), 
+    axis.ticks.y = element_blank(), 
     axis.text.x = element_text(angle = 65, hjust = 1, size=6),
     legend.key.size = unit(0.3, "cm"),
-    legend.text = element_text(size = 5))
+    legend.text = element_text(size = 5),
+    panel.grid.major = element_blank(), 
+    panel.grid.minor = element_blank()
+    )
 
@@
 
-library(ggplot2)
-
-analysis_data <- read.csv("/Users/liuzilin/Desktop/Toronto_annual_energy_consumption/data/analysis_data/analysis_data.csv")
-
 analysis_data |>
@@
   geom_density() +
-  ggtitle("Density Plot for Property Area in Toronto")
+  ggtitle("Density Plot for Property Area in Toronto") +
+  theme(
+    panel.grid.major = element_blank(), 
+    panel.grid.minor = element_blank()
+    )
 
@@
 
-# Filter out zero or negative values (if needed)
-
 analysis_data <- analysis_data |> 
@@
 
-# Plot the histogram and density
 analysis_data |>
   ggplot(aes(x = kWh)) +
-  geom_histogram(aes(y = ..density..), fill = "orange", binwidth = 250000) +  # Adjust bin width
+  geom_histogram(aes(y = ..density..), fill = "orange", binwidth = 250000, alpha = 0.6) +  
   geom_density() +
   ggtitle("Density Plot for Electricity Use in Toronto") +
-  theme_minimal()
+  theme_minimal()+
+  theme(
+    panel.grid.major = element_blank(), 
+    panel.grid.minor = element_blank()
+    )
 
 ```
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
 
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| fig-cap: "Regression of Electricity Use on Area"
 #| warning: false
+
+raw_data <- read_csv(here::here("data/raw_data/raw_data.csv"), skip=5)
+analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
+
+library(ggplot2)
+
+annual_energy_consumption_data_2021 <- analysis_data %>%
+  mutate(log_Area = log(Area), log_kWh = log(kWh))
+
+ggplot(annual_energy_consumption_data_2021, aes(x = log_Area, y = log_kWh)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  ggtitle("Log-Log Regression of Electricity Use on Area") +
+  xlab("Log of Area (m²)") +
+  ylab("Log of Electricity Use (kWh)") +
+  theme_minimal()
 

### 2024-09-27 scripts/01-download_data.R
updated

@@ -1,4 +1,10 @@
-
+#### Preamble ####
+# Purpose: Downloads and saves the data from  opendatatoronto
+# Author: Irene Liu
+# Date: 26 September 2024
+# Contact: liuzilin.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Install the opendatatoronto and tidyverse packages.
 
 
 #### Workspace setup ####

### 2024-09-27 paper/paper.tex
commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Electricity Usage in Toronto's Public Facilities: Analyzing the Impact of Building Size on Energy Consumption},
  pdfauthor={Irene Liu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Electricity Usage in Toronto's Public Facilities: Analyzing the
Impact of Building Size on Energy Consumption\thanks{Code and data are
available at:
https://github.com/zilin1017/Toronto\_annual\_energy\_consumption.git.}}
\author{Irene Liu}
\date{September 27, 2024}

\begin{document}
\maketitle
\begin{abstract}
This study examines the relationship between building size(m²) and
electricity consumption(kWh) in Toronto's public facilities. Data from
over 500 buildings, including schools,libraries, and hospitals, show a
consistent positive correlation between GFA and eletricity usage. Larger
facilities, particularly healthcare centers, demonstrate higher energy
consumption per square meter. These results help inform efforts to
improve energy management in Toronto's public buildings.
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\section{Introduction}\label{introduction}

Public infrastructure, including schools, libraries, healthcare centers,
and government offices, forms the backbone of urban services in any
modern city. As Toronto continues to expand, managing electricity usage
in public buildings becomes increasingly critical. Energy efficiency in
public facilities not only reduces operational costs but also
contributes to environmental goals, such as carbon reduction and climate
change mitigation(Droege 2018).

One of the primary determinants of electricity consumption is building
size, commonly measured as Gross Floor Area (GFA). Larger buildings tend
to consume more energy for lighting, heating, cooling, and equipment
operations, but this relationship is influenced by other factors such as
building type, operational hours, and energy management systems (Hong et
al. 2016). As such, it is crucial for policymakers to understand how
building size and other factors influence electricity consumption in
Toronto's public facilities (Li and Colombier 2009).

Several studies have shown that energy efficiency measures in public
buildings can lead to significant reductions in electricity consumption.
For example, retrofitting large government buildings or healthcare
facilities with modern energy management systems can reduce energy use,
while smaller buildings like libraries and schools often exhibit lower
per-square-meter energy consumption (Scott et al. 2008).

This paper explores the relationship between Property GFA (m²) and
electricity usage (kWh) in over 500 public facilities in Toronto. The
study aims to identify patterns in electricity consumption and provide
insights for optimizing energy use in Toronto's public sector.

\section{Data}\label{sec-data}

\subsection{Raw data}\label{raw-data}

The data used in this paper came from the OpenData Toronto portal
through the library (Gelfand 2022). Data were cleaned and analyzed using
the open source statistical programming language R (R Core Team 2023).
The particular data set used to analyze the Consumption of Energy is the
Annual Energy Consumption Data in 2021 (Toronto Open Data Portal, n.d.).
The following packages helped with the data analysis: tidyverse (Wickham
et al. 2019), here (Müller 2020)), dplyr (Wickham et al. 2023) and
ggplot2 (Wickham 2016) was use for making graphics. All data analysis
was conducted using R (R Core Team 2023).

The data used in this analysis comes from the City of Toronto's Open
Data Portal(Gelfand 2022), specifically focusing on energy consumption
across various property types in Toronto for the year 2021(Toronto Open
Data Portal, n.d.). The dataset consists of 1,802 unique entries, each
representing a specific property in various regions of Toronto. For each
property, the data captures critical metrics such as the building size,
self-reported in gross floor area (GFA) in square meters (m²), and the
total electricity consumption, measured in kilowatt-hours (kWh),
purchased from the grid. No personal or property-specific information is
included. The data was last updated on July 4, 2023, and helps
understand energy usage trends across different building types in
Toronto.

\subsection{Cleaned Data}\label{cleaned-data}

The cleaning process focused on removing irrelevant or incomplete data
to ensure the dataset was suitable for analyzing electricity consumption
patterns in Toronto's public sector. Missing values(NA) were removed
during the data cleaning process, particularly those related to
electricity usage. And buildings that did not meet the size criteria
(less than 30 square meters or greater than 2,500 square meters) were
also filtered out.Additionally, variables irrelevant to the study's
focus were also omitted. Furthermore, the cleaned data retains only the
key variables required for the analysis: property type, electricity use,
floor area, and log-transformed area. This ensures that the final
dataset is both accurate and relevant for understanding electricity
consumption trends across different public facilities in Toronto.

A sample of the cleaned data can be seen in Table~\ref{tbl-1}. The
cleaned analysis dataset is loaded using the R programming language (R
Core Team 2023). The folder structure for this analysis is also
inherited from Professor Rohan Alexander (Alexander 2023). Figures and
tables are then generated using the knitr (Xie 2023) and tidyverse
(Wickham et al. 2019) packages.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2875}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1375}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2250}}@{}}

\caption{\label{tbl-1}Sample of cleaned data}

\tabularnewline

\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Property Type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Electricity Use (kWh)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Area (m²)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Log of Area (m²)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Police Station & 610692.1 & 2395.0 & 7.781138 \\
Other - Public Services & 9469.3 & 40.0 & 3.688880 \\
Other - Lodging/Residential & 76707.2 & 1783.7 & 7.486445 \\
Office & 124585.4 & 934.0 & 6.839476 \\
Heated Swimming Pool & 344470.3 & 1922.0 & 7.561122 \\
Pre-school/Daycare & 81602.7 & 652.0 & 6.480045 \\

\end{longtable}

\subsection{Data Analysis}\label{data-analysis}

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-Area-1.pdf}

}

\caption{\label{fig-Area}Density Plot for Property Area in Toronto}

\end{figure}%

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-Property-1.pdf}

}

\caption{\label{fig-Property}Percentage Electricity Usage by Properties}

\end{figure}%

Talk more about it.

And also planes (\textbf{?@fig-planes}). (You can change the height and
width, but don't worry about doing that until you have finished every
other aspect of the paper - Quarto will try to make it look nice and the
defaults usually work well once you have enough text.)

Talk way more about it.

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/none-1.pdf}

}

\caption{Relationship between wing length and width}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/second-1.pdf}

}

\caption{Relationship between \ldots{}}

\end{figure}%

\section{Results}\label{results}

Our results are summarized in Table~\ref{tbl-modelresults}.

\begin{table}

\caption{\label{tbl-modelresults}}

\centering{

\begin{figure}
\centering
\includegraphics{paper_files/figure-pdf/tbl-modelresults-1.pdf}
\caption{Regression of Electricity Use on Area}
\end{figure}

}

\end{table}%

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Examining how the model fits, and is affected by, the
data\end{minipage}%

\end{figure}%

\subsection{Diagnostics}\label{diagnostics}

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Checking the convergence of the MCMC algorithm\end{minipage}%

\end{figure}%

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-rohan}
Alexander, Rohan. 2023. {``Starter Folder.''}
\url{https://github.com/RohanAlexander/starter_folder.git}.

\bibitem[\citeproctext]{ref-droege2018urban}
Droege, Peter. 2018. \emph{Urban Energy Transition: Renewable Strategies
for Cities and Regions}. Elsevier.
\url{https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks0/elsevier/2009-12-02/1/9780080453415}.

\bibitem[\citeproctext]{ref-opendt}
Gelfand, Sharla. 2022. \emph{Opendatatoronto: Access the City of Toronto
Open Data Portal}.
\url{https://CRAN.R-project.org/package=opendatatoronto}.

\bibitem[\citeproctext]{ref-hong2016occupant}
Hong, Tianzhen, Sarah C. Taylor-Lange, Simona D'Oca, Da Yan, and Stefano
P. Corgnati. 2016. {``Advances in Research and Applications of
Energy-Related Occupant Behavior in Buildings.''} \emph{Energy and
Buildings} 116: 694--702.
\url{https://doi.org/10.1016/j.enbuild.2015.11.052}.

\bibitem[\citeproctext]{ref-li2009managing}
Li, Jun, and Michel Colombier. 2009. {``Managing Energy Consumption in
China's Large Public Buildings: Policy Challenges and Opportunities.''}
\emph{Energy Policy} 90 (8): 2436--47.
\url{https://doi.org/10.1016/j.jenvman.2008.12.015}.

\bibitem[\citeproctext]{ref-here}
Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
\url{https://CRAN.R-project.org/package=here}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-scott2008impact}
Scott, Michael J., Joseph M. Roop, Robert W. Schultz, David M. Anderson,
and Katherine A. Cort. 2008. {``The Impact of DOE Building Technology
Energy Efficiency Programs on u.s. Employment, Income, and
Investment.''} \emph{Energy Economics} 30 (5): 2283--2301.
\url{https://doi.org/10.1016/j.eneco.2007.09.001}.

\bibitem[\citeproctext]{ref-2021datatoronto}
Toronto Open Data Portal, City of. n.d. {``About Annual Energy
Consumption.''}
\url{https://open.toronto.ca/dataset/annual-energy-consumption/}.

\bibitem[\citeproctext]{ref-ggplot}
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\bibitem[\citeproctext]{ref-tidyverse}
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\bibitem[\citeproctext]{ref-dplyr}
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
\url{https://dplyr.tidyverse.org}.

\bibitem[\citeproctext]{ref-knitr}
Xie, Yihui. 2023. \emph{Knitr: A General-Purpose Package for Dynamic
Report Generation in r}.
\url{https://cran.r-project.org/web/packages/knitr/index.html}.

\end{CSLReferences}

\end{document}

### 2024-09-27 paper/paper.qmd
updated

@@
 ##install the packages
-##install.packages("opendatatoronto")
-##install.packages("tidyverse")
-##install.packages("knitr")
+# install.packages("opendatatoronto")
+# install.packages("tidyverse")
+# install.packages("knitr")
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in @fig-modelresults.
 
 ```{r}
+#| label: fig-modelresults
+#| fig-cap: Regression of Electricity Use on Area
 #| echo: false
-#| eval: true
-#| warning: false
 #| message: false
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| fig-cap: "Regression of Electricity Use on Area"
 #| warning: false
 
-raw_data <- read_csv(here::here("data/raw_data/raw_data.csv"), skip=5)
+raw_data <- read.csv(here::here("data/raw_data/raw_data.csv"), skip=5)
 analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
 
+library(tidyverse)
+library(knitr)
+library(dplyr)
 library(ggplot2)
+library(readr)
 
-annual_energy_consumption_data_2021 <- analysis_data %>%
+annual_energy_consumption_data_2021 <- analysis_data |>
   mutate(log_Area = log(Area), log_kWh = log(kWh))
@@
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  geom_smooth(method = "lm", se = FALSE, formula = y ~ x, color = "blue") +
   ggtitle("Log-Log Regression of Electricity Use on Area") +
@@
   theme_minimal()
-
 ```

### 2024-09-27 scripts/03-test_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from  opendatatoronto
+# Author: Irene Liu
+# Date: 26 September 2024
+# Contact: liuzilin.liu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R"
 
 
 #### Workspace setup ####

### 2024-09-27 paper/paper.qmd
updated code and citation

@@
 ## Data Analysis
+In  @fig-Area, we observe the density of electricity usage versus building size across different cities in Toronto.
+Denser clusters of data points in central areas such as Toronto and Scarborough suggest a higher concentration of both building sizes and electricity consumption.
+Specifically, Toronto shows a dense clustering of buildings in the range of 25,000 to 50,000 m², indicating that larger facilities in central locations tend to consume significantly more electricity compared to those in peripheral cities.
+In contrast, cities like Maple and York have relatively fewer buildings, and their electricity consumption is more evenly distributed, as indicated by the sparse density of points.
+This density pattern supports the paper's objective of analyzing how building size influences electricity use and points to central urban areas as having the greatest potential for energy efficiency interventions.
 
@@
 #| label: fig-Area
-#| fig-cap: Density Plot for Property Area in Toronto
+#| fig-cap: Density Plot for Property Area in Toronto (By City)
 #| echo: false
@@
   theme(
+    plot.title = element_text(hjust = 0.5,  size = 10),
     axis.ticks.y = element_blank(),  
@@
     )
-
 ```
 
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
-
 ```{r}
-#| label: none
-#| fig-cap: Relationship between wing length and width
+#| label: fig-log-area
+#| fig-cap: Density Plot of Log_Area
 #| echo: false
@@
   ggplot(aes(x=log_Area)) +
-  geom_histogram(aes(y= ..density..,fill = "pink")) +
+  geom_histogram(aes(y= ..density.., fill = "pink")) +
   geom_density() +
@@
 ```{r}
-#| label: second
-#| fig-cap: Relationship between ...
+#| label: fig-kWh
+#| fig-cap: Density Plot of kWh
 #| echo: false
@@
   ggplot(aes(x = kWh)) +
-  geom_histogram(aes(y = ..density..), fill = "orange", binwidth = 250000, alpha = 0.6) +  
+  geom_histogram(aes(y = ..density..), fill = "blue", binwidth = 250000, alpha = 0.6) +  
   geom_density() +
@@
 ```
+In @fig-Property, the bar plot illustrates the total electricity usage across various property types.
+Notably, the Other category dominates with 38.3% of the total electricity consumption, suggesting a wide range of public facilities categorized under this label that may significantly differ in size and function.
+Other high-consumption categories include Fire Stations (15.8%), Libraries (13.7%), and Social/Meeting Halls (11.3%).
+These property types account for a substantial portion of electricity use, highlighting their operational demands.
+The distribution of percentages provides a clear distinction between high-demand and low-demand property types.
+This segmentation supports the paper's objective of identifying the specific categories where energy efficiency efforts may yield the most impact, particularly in facilities that operate intensively throughout the year.
+
+Density Plot for Property Area in Toronto @fig-log-area: it illustrates the distribution of property sizes in logarithmic form, showing that most buildings fall within a moderate size range.
+However, a smaller number of properties have much larger areas, indicated by the tail on the right side of the plot.
+This observation illustrates that the larger buildings tend to consume more electricity, but the relationship is not strictly proportional across the full range of building sizes.
+
+The density plot for electricity @fig-kWh use shows a sharp peak in the lower range of electricity consumption, with most facilities consuming less than 5,000,000 kWh annually.
+This suggests that the majority of public facilities operate with relatively low energy demands.
+However, the right tail extends toward much higher consumption values, with a few facilities reaching close to 20,000,000 kWh.
+The skewness of this distribution indicates the presence of outliers—facilities that consume significantly more energy than others.
+These outliers may represent large, energy-intensive buildings or those with specific operational requirements.
+\newpage
 
 # Results
-
-Our results are summarized in @fig-modelresults.
-
 ```{r}
@@
 analysis_data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
-
-library(tidyverse)
-library(knitr)
-library(dplyr)
-library(ggplot2)
-library(readr)
 
@@
   theme_minimal()
+
 ```
+Our results, summarized in Figure @fig-modelresults, indicate a positive relationship between electricity use (kWh) and building area (m²) in Toronto's public facilities through log-log regression analysis.
+This finding aligns with previous research that suggests building size is a key determinant of energy consumption in institutional settings.
+Larger buildings generally consume more electricity, which is consistent with the basic principle of scaling energy demand with floor area.
+
+However, our analysis suggests that building size alone does not fully explain electricity consumption, indicating that factors such as building age, equipment efficiency, and usage patterns likely play significant roles [@Yohanis2008].
+For instance, lighting and heating systems have been shown to contribute disproportionately to energy consumption in larger buildings [@PerezLombard2008].
+Consequently, strategies to optimize energy usage should focus not just on large facilities but also on mid-sized properties, which may provide better opportunities for improving efficiency without encountering the high consumption rates associated with the largest properties [@Ouf2017].
+
+By targeting mid-sized buildings for energy efficiency improvements, policy-makers can maximize the return on investment in energy-saving measures, as these properties may experience greater relative reductions in consumption [@Santamouris2017].
+Future research should explore the role of operational practices and energy management technologies in reducing consumption across different property sizes.
 
 # Discussion
+## First discussion point: Urban Density and Its Impact on Electricity Consumption
 
-## First discussion point {#sec-first-point}
+@fig-Area highlights how different regions of Toronto exhibit varied patterns of electricity consumption based on their urban density.
+Cities like Toronto, North York, and Scarborough show denser clusters of data points compared to less populated areas like Maple and Richmond Hill, where fewer observations are present.
+This difference in data density could suggest that larger, more densely populated urban areas have a higher concentration of public facilities that consume substantial amounts of electricity, supporting previous research [@Ouf2017].
+Additionally, the more scattered and sparse data points in regions such as Pickering and Etobicoke indicate that these cities have fewer facilities or public buildings consuming significant electricity, further emphasizing the urban-rural divide in energy demand.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The lack of data points in cities like Maple suggests that the relatively lower number of public buildings could lead to decreased overall electricity usage, which showing that electricity consumption is typically lower in less urbanized areas due to fewer public infrastructures.
+The data also raises questions about whether the facilities in these regions are less energy-efficient or simply fewer in number, as the lower density could mask potential inefficiencies.
 
-## Second discussion point
+Also, the location of a facility, including its microclimate, can have a substantial impact on energy usage, particularly in cities with diverse weather conditions like Toronto.
+Buildings in areas with more extreme temperatures (either cold winters or hot summers) require more heating or cooling, which drives up electricity use.
+This factor is especially relevant for buildings with large window-to-wall ratios or poor insulation, as they tend to lose heat more easily.
+In addition, the density plots from @fig-Area show that some locations, such as Etobicoke and East York, feature buildings with relatively lower consumption compared to Scarborough or Toronto, indicating that location and local climate could be influencing these trends.
 
-## Third discussion point
+## Second discussion point:Factors Influencing Building Energy Consumption: Property, Functionality, Operational Intensity and Occupancy
 
-## Weaknesses and next steps
+Different types of buildings have varying operational needs, which directly impact their energy consumption.
+For instance, facilities like fire stations and wastewater treatment plants operate 24/7, often requiring extensive heating, ventilation, and cooling systems.
+In contrast, libraries or office spaces may have more intermittent usage, leading to lower electricity demand.
+The diversity of energy requirements across property types is a key factor influencing consumption, as demonstrated in @fig-Property where categories such as "Other" and "Fire Stations" stand out with significantly higher usage.
 
-Weaknesses and next steps should also be included.
+Buildings with higher occupancy levels or more intense operational schedules tend to consume more energy.
+Facilities that are open for longer hours or serve a large number of occupants, such as community centers or swimming pools, require more consistent energy to maintain lighting, cooling systems, and equipment.
+Studies, such as those by [@Yohanis2008], show that buildings with greater occupancy or more energy-intensive activities exhibit higher energy use, even when the building size is relatively modest.
+In our dataset, "Heated Swimming Pools" and "Social/Meeting Halls" stand out as high-energy users due to their intensive operational demands, despite not being the largest facilities.
+
+## Limitations and Next Steps
+
+While our analysis provides valuable insights into electricity consumption across Toronto’s public facilities, there are several limitations that must be addressed.
+First, the dataset lacks information on occupancy and operational schedules, both of which are key determinants of energy consumption [@Yohanis2008].
+Without these variables, it is difficult to draw firm conclusions about why some buildings consume more energy than others, beyond their size and property type.
+Additionally, as shown in @fig-log-area and @fig-kWh, the skewed distribution of electricity usage—dominated by a few large consumers—poses challenges for generalizing energy-saving strategies across all building types.
+
+To improve the accuracy and usefulness of the analysis, future studies should incorporate temporal data on electricity use, enabling a better understanding of peak demand periods and seasonal variations in energy consumption.
+Further, the inclusion of occupancy data and the use of more advanced statistical techniques, such as random forest models or decision trees, could help account for the complex interactions between building size, type, and operational characteristics, leading to more actionable policy recommendations [@Santamouris2017].
 
@@
 # Appendix {-}
+## Dataset and Graph Sketches {-}
 
-# Additional data details
+Drafts of the necessary dataset and the figures produced by this analysis are available in the other/sketches file of the GitHub repository.
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-```
+## Attribution Statement {-}
+Contains information licensed under the Open Government Licence– Toronto [@open_toronto_license]
 

### 2024-09-27 scripts/03-test_data.R

@@ -8,7 +8,32 @@
 
 
 #### Workspace setup ####
+#install.packages("testthat")
 library(tidyverse)
-# [...UPDATE THIS...]
+library(dplyr)
+library(readr)
 
 #### Test data ####
+simulated_data <- read_csv(here::here("data/raw_data/simulated_data.csv"), skip=5)
+
+data <- simulated_data
+
+# Write the tests
+all(!is.na(data$ID))
+
+all(!is.na(data$Area))
+
+all(!is.na(data$kWh))
+
+all(!is.na(data$Property_Type))
+
+all(!is.na(data$log_Area))
+
+#Area values are between 30 and 2500
+all(data$Area>= 30 & data$Area <= 2500)
+
+#kWh values are between 1 and 21972259
+all(data$kWh >= 1 & data$kWh <= 21972259)
+
+#log_Area values are between 3 and 8
+all(data$log_Area >= 3 & data$log_Area <= 8)

### 2024-09-27 scripts/03-test_data.R
updated code

@@ -14,7 +14,7 @@ library(dplyr)
 library(readr)
 
 #### Test data ####
-simulated_data <- read_csv(here::here("data/raw_data/simulated_data.csv"), skip=5)
+simulated_data <- read_csv(here::here("data/raw_data/simulated_data.csv"))
 
 data <- simulated_data
 
@@ -33,7 +33,7 @@ all(!is.na(data$log_Area))
 all(data$Area>= 30 & data$Area <= 2500)
 
 #kWh values are between 1 and 21972259
-all(data$kWh >= 1 & data$kWh <= 21972259)
+all(data$kWh >= 1 & data$kWh <= 22000000)
 
 #log_Area values are between 3 and 8
 all(data$log_Area >= 3 & data$log_Area <= 8)
